### 2022-03-29 README.Rmd
added range_matrix and space attributes, removed default range, rebuild palettes

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support three types: *categorical* (qualitative) palettes, *sequential* palettes, and *diverging* palettes. In the near future, more palette types will be added, such as *cyclic*, *bivariate*, and *hierarchical*.

@@

* `c4a_series_add` Add color palettes
* `c4a_series_remove` Remove color palettes
* `c4a_sysdata_import` Import system data
* `c4a_sysdata_export` Export system data

>>>>

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support several types: *categorical* (qualitative) palettes, *sequential* palettes, *diverging* palettes, and *bivariate* palettes (divided into three types). In the near future, more palette types may be added, such as *cyclic* and *hierarchical*.

@@

* `c4a_palettes_add` Add color palettes
* `c4a_palettes_remove` Remove color palettes
* `c4a_sysdata_import` Import system data
* `c4a_sysdata_export` Export system data
